---
format:
  pdf:
    toc: false
    number-sections: false
    colorlinks: true
    documentclass: scrartcl
    papersize: letter
    pdf-engine: xelatex
    fontsize: 10pt
    geometry:
      - margin=1in
      - heightrounded
    include-in-header:
      - preamble.tex
execute:
  warning: false
  echo: false
  message: false
  eval: true
---

```{r}
#| name: setup
#| include: false
#| message: false
#| eval: true

knitr::opts_chunk$set(
  fig.path = "figs/",
  fig.width = 7.252,
  fig.height = 4,
  comment = "#>",
  fig.retina = 3
)

source("functions.R")

# Store IDs
gscholar_id <- 'DY2D56IAAAAJ'
gscholar_page <- paste0("https://scholar.google.com/citations?user=", gscholar_id)
```

\par\centering{\LARGE{Weisi Chen}}
\par\centering{Data Analyst}
\vspace{-5pt}
\par\centering{The university of New South Wales}
\vspace{-5pt}
\par\centering{School of population health}
\vspace{-5pt}
\par\centering{Sydney NSW 2033, Australia}
\vspace{-5pt}
\par\centering{{\large\Telefon} 0452476995}
\vspace{-5pt}
\par\centering{{\large\Letter} weisi.0816@gmail.com}
\vspace{-5pt}

\vspace{-10pt}


# Profile

\vspace{-10pt}
\begin{longtable}{llp{15cm}}
Hard-working and highly disciplined professional with a strong passion for\\ programming, data analysis, data visualization, and statistical modeling.\\ Leveraging a unique blend of training in pharmacy and health data science,\\
I specialize in deriving actionable insights from complex datasets.\\
My current interest lies in population-level analysis using linked data \\
to drive impactful health decisions and inform evidence-based strategies.
\end{longtable}

\vspace{-10pt}


# Work experience

\vspace{-10pt}
\begin{longtable}{llp{15cm}}
July 2023 - Present & \textbf{The university of NSW}, Sydney, NSW & \\
 & Data scientist, School of population health\\[5pt]

Feb 2023 - Dec 2023 & \textbf{The university of Sydney}, Sydney, NSW & \\
 & Data scientist/research officer, School of pharmacy\\
\end{longtable}

\vspace{-10pt}


# Education & Training

\vspace{-10pt}
\begin{longtable}{lll}

    2023 & The university of New South Wales, & M.S health data science\\

    \multicolumn{3}{l}{Dissertation: \emph{Changes in atherosclerotic cardiovascular disease risk over time among people living with HIV}}\\
    
    2019 & The university of Sydney & B.S. Pharmacy\\

\end{longtable}

\vspace{-10pt}

# Research Interests

- **Programming \& Data Analytics**
- **Data linkage studies using population-level data**
- **Pharmaco-epidemiology**

\vspace{-10pt}


# Skills

- **Complex data analysis**
- **Data visualization**
- **Statistical modelling**
- **SAS**
- **R**

\vspace{-10pt}



# Publications

<!-- Set spacing in between list -->

\apptocmd{\tightlist}{\setlength{\itemsep}{4pt}}{}{}

[Google Scholar Profile](https://scholar.google.com.au/citations?user=iCapTGoAAAAJ&hl=en)


## A. Refereed Journal Articles

```{r}
pubs <- get_cv_sheet('pubs') %>%
  mutate(
    journal  = ifelse(is.na(journal), '', paste0('_', journal, '_.')),
    number   = ifelse(is.na(number), '', paste0(number, '.')),
    doi      = ifelse(
               is.na(doi), '',
               paste0('DOI: [', doi, '](', 'https://doi.org/', doi, ')')),
    year     = paste0("(", year, ")"),
    title    = enquote(title),
    citation = paste(author, year, title, journal, number, doi)
  ) %>% 
  arrange(desc(pub_date))
```

```{r}
#| results: asis

make_ordered_list_filtered(pubs, "peer_reviewed")
```



