---
format:
  pdf:
    toc: false
    number-sections: false
    colorlinks: true
    documentclass: scrartcl
    papersize: letter
    pdf-engine: xelatex
    fontsize: 10pt
    geometry:
      - margin=1in
      - heightrounded
    include-in-header:
      - preamble.tex
execute:
  warning: false
  echo: false
  message: false
  eval: true
---

```{r}
#| name: setup
#| include: false
#| message: false
#| eval: true

knitr::opts_chunk$set(
  fig.path = "figs/",
  fig.width = 7.252,
  fig.height = 4,
  comment = "#>",
  fig.retina = 3
)

source("functions.R")

# Store IDs
gscholar_id <- 'DY2D56IAAAAJ'
gscholar_page <- paste0("https://scholar.google.com/citations?user=", gscholar_id)
```

\par\centering{\LARGE{Weisi Chen}}
\par\centering{Data Scientist}
\vspace{-5pt}
\par\centering{Kensington, NSW 2033, Australia}
\vspace{-5pt}
\par\centering{{\large\Telefon} 0452476995}
\vspace{-5pt}
\par\centering{{\large\Letter} weisi.s.chen@sydney.edu.au | weisi.0816@gmail.com}
\vspace{-5pt}
\par\centering{\href{https://github.com/WeisiChen1995}{github.com/WeisiChen1995}}

\vspace{-10pt}


# Profile

\vspace{-10pt}
\begin{longtable}{llp{15cm}}
I am a highly disciplined and hard-working individual professional with a strong passion for\\ technology, programming, data analysis, data visualization, and statistical modeling.\\ Leveraging a unique blend of training in pharmacy and health data science,\\
I specialize in deriving actionable insights from complex health datasets.\\[10pt]

I am proficient in statistical software such as R and SAS, and have extensive experience\\
using these tools for data analysis, visualiztaion, and statistical modelling. \\
I am deeply committed to continuous learning and professional development, \\
always eager to explore new packages, techniques, or skills that can enhance my ability\\
to analyze data effectively and deliver meaningful insights.\\[10pt]

My current interest lies in population-level analysis using linked health data \\
to drive impactful health decisions and inform evidence-based strategies.\\
I thrive on tackling challenging problems with analytical precision and creativity,\\
always striving to deliver impactful results in every project I undertake.\\

\end{longtable}

\vspace{-10pt}


# Education 

\vspace{-10pt}
\begin{longtable}{lll}

    \textbf{Sept 2021 - March 2023} & \textbf{University of New South Wales} & \textbf{M.S. Health Data Science} \\
    & & WAM: 88\% \\
    \multicolumn{3}{l}{\textit{Dissertation: Changes in atherosclerotic cardiovascular disease risk over time among people living with HIV}} \\[10pt]

    \textbf{March 2015 - March 2019} & \textbf{University of Sydney} & \textbf{B.S. Pharmacy} \\


\end{longtable}

\vspace{-10pt}


# Employment History

\vspace{-10pt}
\begin{longtable}{llp{14cm}}

    \textbf{July 2023 - Present} & \textbf{University of New South Wales}, Sydney, NSW & \\
    & \textbf{Data Scientist}, School of Population Health \\[5pt]
    & \multicolumn{2}{l}{I contributed to two projects in this role:} \\
    & 1) ACCESS: Aboriginal Community Controlled Ear Health Support System: \\
    & \hspace{15pt} Developing, embedding, and evaluating best practice models of care. \\[5pt]
    & 2) Evaluation of Sustaining NSW Families, NSW Health. \\[10pt]
    & My role included: \\
    & - Critically reviewed the literature on epidemiological and statistical methods\\
    & to inform the development of analysis plans.\\[5pt]
    & - Drafted data management and data analysis plans, with input from the research team.\\[5pt]
    & - Implemented the data management plan to prepare analysis-ready datasets from linked  \\
    & datasets, including data cleaning and manipulation, using software R and SAS.\\[5pt]
    & - Executed statistical analysis of linked data, with academic supervision,\\       & using statistical packages R and SAS.\\[5pt]
    & - Drafted scientific papers, protocols and conference abstracts, with academic supervision. \\[5pt]
    & - Contributed to the project management of research projects to the highest scientific\\
    & and ethical standards. \\[5pt]
    & - Drafted applications and contribute to ongoing reporting to the relevant ethics committees\\
    & and data custodians for research projects.\\[5pt]
    & - Maintained regular communication with project investigators and Aboriginal community \\
    & organizations to ensure the program is delivered in a culturally appropriate manner. \\[10pt]
    
    \textbf{Feb 2023 - Dec 2023} & \textbf{The University of Sydney}, Sydney, NSW & \\
    & \textbf{Data Scientist/Research Officer}, School of Pharmacy \\

\end{longtable}

\vspace{-10pt}


# Publications

<!-- Set spacing in between list -->

\apptocmd{\tightlist}{\setlength{\itemsep}{4pt}}{}{}

[Google Scholar Profile](https://scholar.google.com.au/citations?user=iCapTGoAAAAJ&hl=en)


## Peer-reviewed Journal Articles

```{r}
pubs <- get_cv_sheet('pubs') %>%
  mutate(
    journal  = ifelse(is.na(journal), '', paste0('_', journal, '_.')),
    number   = ifelse(is.na(number), '', paste0(number, '.')),
    doi      = ifelse(
               is.na(doi), '',
               paste0('DOI: [', doi, '](', 'https://doi.org/', doi, ')')),
    year     = paste0("(", year, ")"),
    title    = enquote(title),
    citation = paste(author, year, title, journal, number, doi)
  ) %>% 
  arrange(desc(pub_date))
```

```{r}
#| results: asis

make_ordered_list_filtered(pubs, "peer_reviewed")
```



