---
format:
  pdf:
    toc: false
    number-sections: false
    colorlinks: true
    documentclass: scrartcl
    papersize: letter
    pdf-engine: xelatex
    fontsize: 10pt
    geometry:
      - margin=1in
      - heightrounded
    include-in-header:
      - preamble.tex
execute:
  warning: false
  echo: false
  message: false
  eval: true
---

```{r}
#| name: setup
#| include: false
#| message: false
#| eval: true

knitr::opts_chunk$set(
  fig.path = "figs/",
  fig.width = 7.252,
  fig.height = 4,
  comment = "#>",
  fig.retina = 3
)

source("functions.R")

# Store IDs
gscholar_id <- 'DY2D56IAAAAJ'
gscholar_page <- paste0("https://scholar.google.com/citations?user=", gscholar_id)
```

\par\centering{\LARGE{Weisi Chen}}
\par\centering{Health Data Scientist}
\vspace{-5pt}
\par\centering{Kensington, NSW 2033}
\vspace{-5pt}
\par\centering{{\large\Telefon} 0452476995}
\vspace{-5pt}
\par\centering{{\large\Letter} weisi.0816@gmail.com}
\vspace{-5pt}
\par\centering{\href{https://github.com/WeisiChen1995}{github.com/WeisiChen1995}}

\vspace{-10pt}


# Profile

\vspace{-10pt}
\begin{longtable}{llp{15cm}}
I am a highly disciplined and hard-working professional with a strong passion for\\ 
technology, programming, data analysis, data visualization, and statistical modeling.\\ 
Leveraging a unique blend of training in pharmacy and health data science,\\
I specialize in deriving actionable insights from complex health datasets.\\[10pt]

I am proficient in statistical software such as R and SAS, and have extensive experience\\
using these tools for data analysis, visualization, and statistical modelling. \\
I am deeply committed to continuous learning and professional development, \\
always eager to explore new packages, techniques, or skills that can enhance my ability\\
to analyze data effectively and deliver meaningful insights.\\[10pt]

My current interest lies in population-level analysis using linked health data \\
to drive impactful health decisions and inform evidence-based strategies.\\
I thrive on tackling challenging problems with analytical precision and creativity,\\
always striving to deliver impactful results in every project I undertake.\\

\end{longtable}

\vspace{-10pt}


# Education 

\vspace{-10pt}
\begin{longtable}{lll}

    \textbf{Sept 2021 - March 2023} & \textbf{The University of New South Wales} & \textbf{M.S. Health Data Science} \\
    & & WAM: 88\% (Dissertation: 91\%) \\
    \multicolumn{3}{l}{\textit{Dissertation: Changes in atherosclerotic cardiovascular disease risk over time among people living with HIV}} \\[10pt]

    \textbf{March 2015 - March 2019} & \textbf{The University of Sydney} & \textbf{B.S. Pharmacy} \\


\end{longtable}

\vspace{-10pt}


# Employment History

\raggedright \underline{\textbf{Research-focused Positions}}

\vspace{-10pt}
\begin{longtable}{llp{14cm}}

    \textbf{July 2023 - Present} & \textbf{The University of New South Wales}, Sydney, NSW & \\
    & \textbf{Data Scientist}, School of Population Health \\[5pt]
    & \multicolumn{2}{l}{I contributed to three projects in this role:} \\
    & 1) ACCESS: Aboriginal Community Controlled Ear Health Support System: \\ 
    & \hspace{15pt} Developing, embedding, and evaluating best practice models of care. \\[5pt]
    & 2) Evaluation of Sustaining NSW Families, NSW Health. \\[5pt]
    & 3) Building the NSW Child E-Cohort Project data platform linkage 2, linking:\\[5pt]
    & \hspace{15pt} - Perinatal Data Collection \\
    & \hspace{15pt} - Birth Registrations \\
    & \hspace{15pt} - Hospital Separations \\
    & \hspace{15pt} - Emergency Department Presentations \\
    & \hspace{15pt} - Australian Early Development Census \\
    & \hspace{15pt} - Public School Enrolments \\
    & \hspace{15pt} - NAPLAN \\
    & \hspace{15pt} - Child Protection Reports \\
    & \hspace{15pt} - Out-of-Home Care Placements \\
    & \hspace{15pt} - Justice Data (youth and adult corrections) \\
    & \hspace{15pt} - Public Housing Data \\
    & \hspace{15pt} - Death Registrations/Cause of Death \\[10pt]
    
    & \multicolumn{2}{l}{\textbf{My role included:}} \\[5pt]
    & \multicolumn{2}{p{0.8\textwidth}}{- Critically reviewing the literature on epidemiological and statistical methods to inform the development of analysis plans.} \\[5pt]
    & \multicolumn{2}{p{0.8\textwidth}}{- Drafting data management and data analysis plans, with input from the research team.} \\[5pt]
    & \multicolumn{2}{p{0.8\textwidth}}{- Implementing the data management plan to prepare analysis-ready datasets from linked datasets, including data cleaning and manipulation, using R and SAS software.} \\[5pt]
    & \multicolumn{2}{p{0.8\textwidth}}{- Executing statistical analysis of linked data (e.g., logistic regression and inverse probability of treatment weighting) relevant to the project, using statistical packages R and SAS.} \\[5pt]
    & \multicolumn{2}{p{0.8\textwidth}}{- Drafting scientific papers, protocols, and conference abstracts.} \\[5pt]
    & \multicolumn{2}{p{0.8\textwidth}}{- Contributing to the project management of research projects to the highest scientific and ethical standards.} \\[5pt]
    & \multicolumn{2}{p{0.8\textwidth}}{- Drafting applications and contributing to ongoing reporting to the relevant ethics committees and data custodians for research projects.} \\[5pt]
    & \multicolumn{2}{p{0.8\textwidth}}{- Maintaining regular communication with project investigators and Aboriginal community organizations to ensure the program is delivered in a culturally appropriate manner.} \\[10pt]
    
    \\[10pt] % Add more vertical space before the next section
    
    \textbf{Feb 2023 - Dec 2023} & \textbf{The University of Sydney}, Sydney, NSW & \\
    & \textbf{Data Scientist/Research Officer}, School of Pharmacy, (FTE 0.4) \\[5pt]
    & \multicolumn{2}{l}{In this role, I contributed to the Multi-Agency Data Integration Project (MADIP):} \\
    & \multicolumn{2}{p{0.8\textwidth}}{Investigating high-risk prescribing in Australian older adults using the linked PBS and Census data.} \\[15pt]
    & \multicolumn{2}{l}{\textbf{Key Responsibilities:}} \\[5pt]
    & \multicolumn{2}{p{0.8\textwidth}}{- Preparing analysis-ready datasets from linked datasets, including data cleaning and manipulation, using R software.} \\[5pt]
    & \multicolumn{2}{p{0.8\textwidth}}{- Conducting data analysis and statistical modeling (e.g., logistic regression) relevant to the project.} \\
    & \multicolumn{2}{p{0.8\textwidth}}{- Contributing to publications and conference abstracts.} \\
    & \multicolumn{2}{p{0.8\textwidth}}{- Assisting with ongoing data management and documentations for reproducibility.} \\
 

\end{longtable}

\vspace{-10pt}

\raggedright \underline{\textbf{Clinical-focused Positions}}

\vspace{-10pt}
\begin{longtable}{llp{14cm}}

    \textbf{Mar 2021 - Dec 2023} & \textbf{Bondi Junction Pharmacy}, Sydney, NSW & \\
    & \textbf{Pharmacist in charge (FTE 0.2)}\\[5pt]

    \textbf{Mar 2021 - Dec 2023} & \textbf{Blooms the Chemsit Bondi Junction}, Sydney, NSW & \\
    & \textbf{Pharmacist on duty (FTE 0.4)}\\[5pt]

    \textbf{Mar 2020 - Sept 2020} & \textbf{Chemist Warehouse Double Bay}, Sydney, NSW & \\
    & \textbf{Registered Pharmacist}\\[5pt]

    \textbf{Dec 2018 - Mar 2020} & \textbf{Chemist Warehouse Randwick}, Sydney, NSW & \\
    & \textbf{Graduate Intern Pharmacist}\\[5pt]

\end{longtable}

\vspace{-10pt}


# Research Interests

\vspace{-10pt}
\begin{longtable}{llp{15cm}}
I am passionate about pharmaco-epidemiology, with a particular focus on high-risk medication prescribing\\
using national, population-level linked data. \\[5pt]

I have extensive experience with data analysis, visualization, and statistical modeling tools. \\[5pt]

My goal is to contribute to public health improvement by analyzing and understanding medication prescribing  \\ 
patterns, ultimately informing safer, evidence-based healthcare practices. \\[10pt]

\end{longtable}

\vspace{-10pt}


# Publications

<!-- Set spacing in between list -->

\apptocmd{\tightlist}{\setlength{\itemsep}{4pt}}{}{}

\begin{center}
\href{https://scholar.google.com.au/citations?user=iCapTGoAAAAJ\&hl=en}{Google Scholar Profile}
\end{center}

## A. Peer-reviewed Journal Articles

```{r}
pubs <- get_cv_sheet('pubs') %>%
  mutate(
    journal  = ifelse(is.na(journal), '', paste0('_', journal, '_.')),
    number   = ifelse(is.na(number), '', paste0(number, '.')),
    doi      = ifelse(
               is.na(doi), '',
               paste0('DOI: [', doi, '](', 'https://doi.org/', doi, ')')),
    year     = paste0("(", year, ")"),
    title    = enquote(title),
    citation = paste(author, year, title, journal, number, doi)
  ) %>% 
  arrange(desc(pub_date))
```

```{r}
#| results: asis

make_ordered_list_filtered(pubs, "peer_reviewed")
```

## B. Working Papers

```{r}
#| results: asis

make_ordered_list_filtered(pubs, "working_paper")
```

## C. Working Reports

```{r}
#| results: asis

make_ordered_list_filtered(pubs, "working_report")
```


## D. Contributed Presentations

```{r}
presentations <- get_cv_sheet('presentations') %>%
  arrange(desc(date)) %>% 
  mutate(
    contributors = ifelse(is.na(contributors), '', paste0(', ', contributors)),,
    title = paste0(enquote(title), contributors),
    title = ifelse(is.na(series), title, paste(title, series, sep = '. ')),
    date = paste0(format(as.Date(date), format = "%b %d, %Y"), '.'),
    citation = paste(title, host, location, date, sep = '. ')
  )

```

```{r}
#| results: asis

make_ordered_list_filtered(presentations, "contributed_presentation")
```
