---
format:
  pdf:
    include-in-header: 
      - text: |
          \usepackage{tabularx}
          \usepackage{xcolor}  
          \usepackage{fontawesome5}
      - preamble.tex
    toc: false
    number-sections: false
    colorlinks: true
    documentclass: scrartcl
    papersize: letter
    pdf-engine: xelatex
    fontsize: 10pt
    geometry:
      - margin=1in
      - heightrounded
execute:
  warning: false
  echo: false
  message: false
  eval: true
---


```{r}
#| name: setup
#| include: false
#| message: false
#| eval: true

knitr::opts_chunk$set(
  fig.path = "figs/",
  fig.width = 7.252,
  fig.height = 4,
  comment = "#>",
  fig.retina = 3
)

source("functions.R")

# Store IDs
gscholar_id <- 'DY2D56IAAAAJ'
gscholar_page <- paste0("https://scholar.google.com/citations?user=", gscholar_id)
```
\setlength{\parskip}{0.2em} 
\setlength{\parindent}{1pt} 

\begin{tabular*}{\textwidth}{@{\extracolsep{\fill}} l r}
\begin{tabular}{l}
\textbf{\Huge Weisi Chen} \\[6pt]  % adjust spacing as desired
\textbf{Health Data Analyst} \\[50pt] 
\end{tabular} &
\begin{tabular}{r}
Kensington, NSW 2033 \\
{\large\Telefon} 0452 476 995 \\
\textcolor{black}{\faEnvelope} weisi.0816@gmail.com \\
\faGlobe \hspace{1mm} \href{https://weisichen.org}{weisichen.org} \\
\faGithub \hspace{1mm} \href{https://github.com/WeisiChen1995}{WeisiChen1995}
\end{tabular}
\end{tabular*}
\vspace{-8pt}

\section*{Brief Biography}\vspace{-8pt}
\noindent
I am a data analyst specializing in the analysis of large and complex datasets, with expertise in data mining, visualization, and statistical modeling. I have contributed to research across the fields of biostatistics, clinical epidemiology, and pharmacoepidemiology. With a prior background in pharmacy, I bring a unique combination of domain knowledge and analytical expertise to health data research, enabling me to uncover meaningful insights that inform evidence-based decision-making. \vspace{5pt}

Over the years, I have worked extensively with large, linked administrative health datasets, developing a strong understanding of data integration, quality assurance, and population-level analysis. My work often involves transforming raw, complex data into actionable insights that support health policy and research initiatives. \vspace{-10pt}

\section*{Technical Skills \& Expertise}\vspace{-6pt}
\noindent
R $\cdot$ SAS $\cdot$ R Shiny $\cdot$ Tableau $\cdot$ Power BI $\cdot$ GitHub

Big Data Management $\cdot$ Reproducible Research $\cdot$ Data Visualization $\cdot$ Statistical Analysis $\cdot$ Data Storytelling $\cdot$ Dashboard Development
\normalsize
\vspace{-10pt}

\section*{Education}\vspace{-8pt}
\noindent
\begin{longtable}{@{}p{3.5cm}p{6.5cm}p{5cm}@{}}
\textbf{Sept 2021 - Mar 2023} & \textbf{The University of New South Wales} & \textbf{M.S. Health Data Science} \\
& & WAM: 88\% (Dissertation: 91\%) \\
\multicolumn{3}{@{}l}{\textit{Dissertation: Changes in atherosclerotic cardiovascular disease risk over time among people living with HIV}} \\[2pt]

\textbf{Mar 2015 - Mar 2019} & \textbf{The University of Sydney} & \textbf{B.S. Pharmacy} \\
\end{longtable}
\normalsize
\vspace{-15pt}

\section*{Employment History}\vspace{-8pt}
\subsection*{Data-focused Positions}\vspace{-6pt}

\begin{longtable}{@{}p{3.5cm}p{12cm}@{}}
\textbf{July 2023 - Dec 2023; April 2025 - Present} &
\textbf{Data Scientist / Research Officer, Sydney Pharmacy School, The University of Sydney} \\
\end{longtable}

\begin{itemize}
\setlength\itemsep{0.5em}   % space between items
\setlength\parskip{0.5pt}      % no extra paragraph space inside items
\setlength\parsep{0.5pt}       % no extra paragraph separation
\setlength\topsep{0.5em}     % space above/below list
\item \textbf{Lead analyst, Nationwide study mapping multimorbidity disease clusters in older Australians} using large-scale national linked health administrative datasets. Responsibilities included conducting literature reviews, designing study methods, performing analyses, and developing advanced visualizations (e.g., network clustering using R (\textit{igraph}) package). Outputs included drafting the manuscript as first author and preparing conference abstracts and presentations.
\item \textbf{Developed a comprehensive national dementia cohort} integrating hospital admissions, ED presentations, PBS, MBS, aged care, and death registrations to support future studies.
\item \textbf{Lead analyst, Multi-Agency Data Integration Project (MADIP)} investigating high-risk prescribing patterns in older adults with dementia using linked PBS and Census data. Responsibilities included literature review, study design, descriptive analyses, and logistic regression modelling. Outputs included contributing to manuscripts, conference abstracts, and presentations.
\item \textbf{Collaborated with investigators, research partners, and stakeholders} to ensure timely project delivery.
\end{itemize}


\begin{longtable}{@{}p{3.5cm}p{12cm}@{}}
\textbf{July 2023 - Mar 2025} &
\textbf{Data Scientist / Research Officer, School of Population Health, The University of New South Wales} \\
\end{longtable}


\begin{itemize}
\setlength\itemsep{0.5em}   % space between items
\setlength\parskip{0.5pt}    % no extra paragraph space inside items
\setlength\parsep{0.5pt}     % no extra paragraph separation
\setlength\topsep{0.5em}     % space above/below list

\item \textbf{Lead analyst, Aboriginal Community Controlled Ear Health Support System (ACCESS) project.} Responsibilities included conducting literature reviews, drafting data management and analysis plans with research teams, preparing analysis-ready datasets from linked sources, and performing statistical analyses including descriptive statistics and visualizations to examine ear health patterns among Aboriginal children over time. Contributed to manuscripts, conference abstracts, and presentations.

\item \textbf{Lead analyst, Evaluation of Sustaining NSW Families (NSW Health) project.} Responsibilities included conducting literature reviews, drafting and implementing data management and analysis plans for linked datasets, and performing analyses using target trial emulation with inverse probability of treatment weighting. Contributed to manuscripts, conference abstracts, and presentations.

\item \textbf{Assisted in building a large-scale linked data platform integrating multiple datasets for NSW Child E-Cohort Project}: 
  \begin{itemize}
    \item Perinatal Data Collection, Birth Registrations, Hospital Separations, and ED Presentations
    \item Australian Early Development Census, Public School Enrolments, and NAPLAN
    \item Child Protection Reports, Out-of-Home Care Placements, Justice (Youth \& Adult Corrections), Public Housing, and Death Registrations
  \end{itemize}
 
\item \textbf{Drafted ethics and data access applications}, contributed to ongoing reporting to committees and data custodians, and maintained regular communication with project investigators and Aboriginal community organizations to ensure culturally appropriate program delivery.


\end{itemize}

\subsection*{Clinical-focused Positions}

\begin{longtable}{@{}p{3.5cm}p{12cm}@{}}
\textbf{Mar 2021 - Dec 2023} & \textbf{Pharmacist in Charge (FTE 0.2), Bondi Junction Pharmacy, Sydney, NSW} \\
\textbf{Mar 2021 - Dec 2023} & \textbf{Pharmacist on Duty (FTE 0.4), Blooms the Chemist, Bondi Junction, Sydney, NSW} \\
\textbf{Mar 2020 - Sept 2020} & \textbf{Registered Pharmacist, Chemist Warehouse, Double Bay, Sydney, NSW} \\
\textbf{Dec 2018 - Mar 2020} & \textbf{Graduate Intern Pharmacist, Chemist Warehouse, Randwick, Sydney, NSW} \\
\end{longtable}

\textbf{Key Responsibilities:}
\begin{itemize}
    \item Dispensed medications safely using pharmacy software; reviewed patient histories.
    \item Counseled patients on prescriptions, OTC medications, and medical devices.
    \item Supervised and mentored pharmacy students and technicians.
    \item Prepared blister packs for elderly patients to optimize adherence.
    \item Performed blood pressure tests, provided counseling, and referred patients as needed.
    \item Collaborated with healthcare professionals to optimize patient outcomes.
    \item Reported adverse drug events (ADEs) and medication errors per regulations.
\end{itemize}


\section*{Research Interests}

I am interested in ageing research and pharmacoepidemiology, and in advancing my expertise in statistical and analytical methods using large, linked health administrative datasets.

# Publications

<!-- Set spacing in between list -->

\apptocmd{\tightlist}{\setlength{\itemsep}{4pt}}{}{}

\begin{center}
\href{https://scholar.google.com.au/citations?user=iCapTGoAAAAJ\&hl=en}{Google Scholar Profile}
\end{center}

## A. Peer-reviewed Journal Articles

```{r}
pubs <- get_cv_sheet('pubs') %>%
  mutate(
    journal  = ifelse(is.na(journal), '', paste0('_', journal, '_.')),
    number   = ifelse(is.na(number), '', paste0(number, '.')),
    doi      = ifelse(
               is.na(doi), '',
               paste0('DOI: [', doi, '](', 'https://doi.org/', doi, ')')),
    year     = paste0("(", year, ")"),
    title    = enquote(title),
    citation = paste(author, year, title, journal, number, doi)
  ) %>% 
  arrange(desc(pub_date))
```

```{r}
#| results: asis

make_ordered_list_filtered(pubs, "peer_reviewed")
```

## B. Working Papers

```{r}
#| results: asis

make_ordered_list_filtered(pubs, "working_paper")
```

## C. Working Reports

```{r}
#| results: asis

make_ordered_list_filtered(pubs, "working_report")
```


## D. Contributed Presentations

```{r}
presentations <- get_cv_sheet('presentations') %>%
  arrange(desc(date)) %>% 
  mutate(
    contributors = ifelse(is.na(contributors), '', paste0(', ', contributors)),,
    title = paste0(enquote(title), contributors),
    title = ifelse(is.na(series), title, paste(title, series, sep = '. ')),
    date = paste0(format(as.Date(date), format = "%b %d, %Y"), '.'),
    citation = paste(title, host, location, date, sep = '. ')
  )

```

```{r}
#| results: asis

make_ordered_list_filtered(presentations, "contributed_presentation")
```
