---
format:
  pdf:
    include-in-header: 
      - text: |
          \usepackage{tabularx}
          \usepackage{xcolor}  
          \usepackage{fontawesome5}
      - preamble.tex
    toc: false
    number-sections: false
    colorlinks: true
    documentclass: scrartcl
    papersize: letter
    pdf-engine: xelatex
    fontsize: 10pt
    geometry:
      - margin=1in
      - heightrounded
execute:
  warning: false
  echo: false
  message: false
  eval: true
---


```{r}
#| name: setup
#| include: false
#| message: false
#| eval: true

knitr::opts_chunk$set(
  fig.path = "figs/",
  fig.width = 7.252,
  fig.height = 4,
  comment = "#>",
  fig.retina = 3
)

source("functions.R")

# Store IDs
gscholar_id <- 'DY2D56IAAAAJ'
gscholar_page <- paste0("https://scholar.google.com/citations?user=", gscholar_id)
```
\setlength{\parskip}{0.2em} 
\setlength{\parindent}{1pt} 

\begin{tabular*}{\textwidth}{@{\extracolsep{\fill}} l r}
\begin{tabular}{l}
\textbf{\Huge Weisi Chen} \\[6pt]  % adjust spacing as desired
\end{tabular} &
\begin{tabular}{r}
Kensington, NSW 2033 \\
{\large\Telefon} 0452 476 995 \\
\textcolor{black}{\faEnvelope} weisi.0816@gmail.com \\
\faGithub \hspace{1mm} \href{https://github.com/WeisiChen1995}{WeisiChen1995}
\end{tabular}
\end{tabular*}
\vspace{-8pt}

\section*{Brief Biography}\vspace{-8pt}
\noindent
I hold a postgraduate qualification in Health Data Science (WAM: 88%). Since 2023, I have contributed to research across the fields of biostatistics, clinical epidemiology, and pharmacoepidemiology.\vspace{5pt}

Over the years, I have worked extensively with large, linked administrative health datasets, developing strong expertise in data integration, data quality assurance, and population-level analysis. I have experience working with the SURE, PLIDA, and NHDH data platforms and am proficient in statistical software, including SAS and R.\vspace{-10pt}

\section*{Technical Skills \& Expertise}\vspace{-6pt}
\noindent
SAS $\cdot$ R $\cdot$ R Shiny $\cdot$ GitHub

Big Data Management $\cdot$ Reproducible Research $\cdot$ Data Visualization $\cdot$ Statistical Analysis $\cdot$ Data Storytelling 
\normalsize
\vspace{-10pt}

\section*{Education}\vspace{-8pt}
\noindent
\begin{longtable}{@{}p{3.5cm}p{6.5cm}p{5cm}@{}}
\textbf{Sept 2021 - Mar 2023} & \textbf{The University of New South Wales} & \textbf{M.S. Health Data Science} \\
& & WAM: 88\% (Dissertation: 91\%) \\
\multicolumn{3}{@{}l}{\textit{Dissertation: Changes in atherosclerotic cardiovascular disease risk over time among people living with HIV}} \\[2pt]

\textbf{Mar 2015 - Mar 2019} & \textbf{The University of Sydney} & \textbf{B.S. Pharmacy} \\
\end{longtable}
\normalsize
\vspace{-15pt}

\section*{Employment History}\vspace{-8pt}
\subsection*{Research-focused Positions}\vspace{-6pt}

\begin{longtable}{@{}p{3.5cm}p{12cm}@{}}
\textbf{Mar 2023 - Dec 2023; April 2025 - Present} &
\textbf{Data Scientist / Research Officer, Sydney Pharmacy School, The University of Sydney} \\
\end{longtable}


\setlength\itemsep{0.5em}   
\setlength\parskip{0.5pt}     
\setlength\parsep{0.5pt}     
\setlength\topsep{0.5em}   

\textbf{Lead analyst on national studies using large-scale linked health data to map multimorbidity clusters and high-risk prescribing in older Australians. Experienced in study design, statistical analysis, cohort development, and translating complex data into actionable research outputs.} \vspace{5pt}

\begin{itemize}

\item \textbf{Lead analyst and first author, Multimorbidity clusters among males and females aged 65 years and over in Australia with at least one pharmaceutical or medical service claim: a nationwide cross-sectional data linkage study}. Responsibilities included conducting literature reviews, contributing to study design, performing statistical analyses (including network cluster analysis), developing advanced data visualisations, and drafting the first-author manuscript. Outputs include first-author manuscript accepted for publication in the Medical Journal of Australia and contributing to conference abstracts and presentations. 
\item \textbf{Lead analyst, Multi-Agency Data Integration Project (MADIP)} investigating high-risk prescribing patterns in older adults with dementia using linked PBS and Census data. Responsibilities included literature review, study design, descriptive analyses, and logistic regression modelling. Outputs included contributing to manuscripts, conference abstracts, and presentations.
\item \textbf{Lead analyst, Developed a comprehensive national dementia cohort} integrating hospital admissions, ED presentations, PBS, MBS, aged care, and death registrations
\end{itemize}


\begin{longtable}{@{}p{3.5cm}p{12cm}@{}}
\textbf{July 2023 - Mar 2025} &
\textbf{Data Scientist, School of Population Health, The University of New South Wales} \\
\end{longtable}


\setlength\itemsep{0.5em}   
\setlength\parskip{0.5pt}    
\setlength\parsep{0.5pt}    
\setlength\topsep{0.5em}     

\textbf{Analyst in managing and analyzing large, linked health and social datasets, generating insights through statistical analysis and visualizations. } \vspace{5pt}

\begin{itemize}
\item \textbf{Analyst, Aboriginal Community Controlled Ear Health Support System (ACCESS) project.} Responsibilities included conducting literature reviews, drafting data management and analysis plans with research teams, preparing analysis-ready datasets from linked sources, and performing statistical analyses including descriptive statistics and visualizations to examine ear health patterns among Aboriginal children over time under supervision.

\item \textbf{Analyst, Evaluation of Sustaining NSW Families project.} Responsibilities included conducting literature reviews, drafting and implementing data management and analysis plans for linked datasets, and performing analyses using target trial emulation with inverse probability of treatment weighting under supervision. 

\item \textbf{Assisted in building a large-scale linked data platform integrating multiple datasets for NSW Child E-Cohort Project}. 

\end{itemize}


\section*{Research Interests}

My research interests involve in ageing, multimorbidity clusters and trajectories, and high-risk prescribing, with a particular focus on developing and applying advanced statistical and analytical methods to large-scale linked health administrative data.

# Publications

<!-- Set spacing in between list -->

\apptocmd{\tightlist}{\setlength{\itemsep}{4pt}}{}{}

\begin{center}
\href{https://scholar.google.com.au/citations?user=iCapTGoAAAAJ\&hl=en}{Google Scholar Profile}
\end{center}

## A. Peer-reviewed Journal Articles

```{r}
pubs <- get_cv_sheet('pubs') %>%
  mutate(
    journal  = ifelse(is.na(journal), '', paste0('_', journal, '_.')),
    number   = ifelse(is.na(number), '', paste0(number, '.')),
    doi      = ifelse(
               is.na(doi), '',
               paste0('DOI: [', doi, '](', 'https://doi.org/', doi, ')')),
    year     = paste0("(", year, ")"),
    title    = enquote(title),
    citation = paste(author, year, title, journal, number, doi)
  ) %>% 
  arrange(desc(first_author), desc(pub_date))
```


```{r}
#| results: asis

make_ordered_list_filtered(pubs, "peer_reviewed")
```
